\documentclass[12pt]{article}\pagestyle{myheadings}

\title{Questionnaire - Part A}

\markright{ Questionnaire - Part A}
\usepackage[a4paper, total={6.3in, 9.7in}]{geometry}
\usepackage{dirtytalk}
\usepackage{mdframed}
\usepackage{amsmath,amssymb,amsthm,amsfonts,graphics}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem*{definition}{Definition}

\renewcommand{\qedsymbol}{\ensuremath{\blacksquare}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}} 

\begin{document}
\begin{mdframed}

\textbf{We are interested in knowing facts about you as well as some of your opinions about
computer programming and mobile game. If you do not wish to answer a question, please skip it and move on to the next question. Ask the survey person for help if you do not understand something or are not sure how
to answer.}

\end{mdframed}
\begin{mdframed}
\begin{enumerate}

\item I like mobile games. \\
$\square$ Strongly disagree $\square$ Disagree $\square$ Neither agree nor disagree \\$\square$ Agree $\square$ Strongly agree

\item On an average day, how many hours do you spend gaming? \\
$\square$ Rarely $\square$ Half an hour	$\square$ 1 hour $\square$ 2 hours $\square$ 3 hours $\square$	4+ hours

\item Did you ever think, \say{I Want to Learn computer programming but I Don't Know where to Start.} \\
$\square$ Strongly disagree $\square$ Disagree $\square$ Neither agree nor disagree\\ $\square$ Agree $\square$ Strongly agree

\item Have you done any computer programming or coding prior to this workshop? \\
$\square$ Yes $\square$ No








\item When I think of people who do coding, I think of \\
$\square$ Mostly girls $\square$ Both girls and boys equally $\square$ Mostly boys

\item Computer programming is harder for me than for most students in my grade.\\
$\square$ Strongly disagree $\square$ Disagree $\square$ Neither agree nor disagree \\$\square$ Agree $\square$ Strongly agree


\item As an adult, I would like to have a job that uses coding. \\ 
$\square$ Strongly disagree $\square$ Disagree $\square$ Neither agree nor disagree\\ $\square$ Agree $\square$ Strongly agree



\item I think learning Computer programming or Coding will help me in my daily life in the future.\\
$\square$ Strongly disagree $\square$ Disagree $\square$ Neither agree nor disagree \\$\square$ Agree $\square$ Strongly agree

\item I like playing mobile games that got a good...\\
$\square$  Gameplay $\square$ Story-line $\square$ Both

\item Having my own avatar made me feel more involved in the game.\\
$\square$ Strongly disagree $\square$ Disagree $\square$ Neither agree nor disagree \\$\square$ Agree $\square$ Strongly agree


\item I like the idea of learning computer programming in Te Reo Maori.\\
$\square$ Strongly disagree $\square$ Disagree $\square$ Neither agree nor disagree \\$\square$ Agree $\square$ Strongly agree\\
\\
\end{enumerate}

\end{mdframed}



\end{document}